\fbox{\begin{minipage}{0.9\textwidth}
\textbf{Key References:} \\
\footnotesize
T.~Apiwattanapong, A.~Orso, and M.~J. Harrold.
\newblock A differencing algorithm for object-oriented programs.
\newblock In {\em ASE '04: Proceedings of the 19th IEEE International
  Conference on Automated Software Engineering}, pages 2--13, Washington, DC,
  USA, 2004. IEEE Computer Society.


A.~Bacchelli and C.~Bird.
\newblock Expectations, outcomes, and challenges of modern code review.
\newblock In {\em Proceedings of the 2013 international conference on software
  engineering}, pages 712--721. IEEE Press, 2013.

J.~R. Cordy.
\newblock The txl source transformation language.
\newblock {\em Science of Computer Programming}, 61(3):190--210, 2006.

D.~R. Engler, D.~Y. Chen, and A.~Chou.
\newblock Bugs as inconsistent behavior: A general approach to inferring errors
  in systems code.
\newblock In {\em Symposium on Operating Systems Principles}, pages 57--72,
  2001.

J.~Henkel and A.~Diwan.
\newblock Catchup!: {Capturing} and replaying refactorings to support api
  evolution.
\newblock In {\em ICSE '05: Proceedings of the 27th International Conference on
  Software Engineering}, pages 274--283, New York, NY, USA, 2005. ACM.

M.~Kim, T.~Zimmermann, and N.~Nagappan.
\newblock A field study of refactoring challenges and benefits.
\newblock In {\em Proceedings of the ACM SIGSOFT 20th International Symposium
  on the Foundations of Software Engineering}, FSE '12, pages 50:1--50:11, New
  York, NY, USA, 2012. ACM.

M.~Kim, V.~Sazawal, D.~Notkin, and G.~Murphy.
\newblock An empirical study of code clone genealogies.
\newblock In {\em Proceedings of the 10th European Software Engineering
  Conference Held Jointly with 13th ACM SIGSOFT International Symposium on
  Foundations of Software Engineering}, ESEC/FSE-13, pages 187--196, New York,
  NY, USA, 2005. ACM.

K.~Prete, N.~Rachatasumrit, N.~Sudan, and M.~Kim.
\newblock Template-based reconstruction of complex refactorings.
\newblock In {\em Software Maintenance (ICSM), 2010 IEEE International
  Conference on}, pages 1 --10. IEEE Press, September 2010.

%T.~Zhang, M.~Song, J.~Pinedo, and M.~Kim.
%\newblock Interactive code review for systematic changes.
%\newblock In {\em Proceedings of the 37th International Conference on Software
%  Engineering-Volume 1}, pages 111--122. IEEE Press, 2015.


X.~Ren, F.~Shah, F.~Tip, B.~G. Ryder, and O.~Chesley.
\newblock Chianti: a tool for change impact analysis of java programs.
\newblock In {\em OOPSLA '04: Proceedings of the 19th annual ACM SIGPLAN
  Conference on Object-Oriented Programming, Systems, Languages, and
  Applications}, pages 432--448, New York, NY, USA, 2004. ACM.

P.~Tarr, H.~Ossher, W.~Harrison, and J.~Stanley M.~Sutton.
\newblock N degrees of separation: multi-dimensional separation of concerns.
\newblock In {\em ICSE '99: Proceedings of the 21st International Conference on
  Software Engineering}, pages 107--119, Los Alamitos, CA, USA, 1999. IEEE
  Computer Society Press.

W.~Weimer, T.~Nguyen, C.~Le~Goues, and S.~Forrest.
\newblock Automatically finding patches using genetic programming.
\newblock In {\em Proceedings of the 31st International Conference on Software
  Engineering}, ICSE '09, pages 364--374, Washington, DC, USA, 2009. IEEE
  Computer Society.

A.~Zeller.
\newblock Yesterday, my program worked. today, it does not. why?
\newblock In {\em ESEC/FSE-7: Proceedings of the 7th European Software
  Engineering Conference held jointly with the 7th ACM SIGSOFT International
  Symposium on Foundations of Software Engineering}, pages 253--267, London,
  UK, 1999. Springer-Verlag.

\end{minipage}}


